### 2016-01-21 AcademicPaperSummaries/PaperSummaries.tex
Added Leighley (1990)

>>>>

\textbf{Leighley, Jan E. 1990. “Social Interaction and Contextual Influences On Political Participation.” American Politics Research 18(4): 459–475.}\\

\underline{Keywords:} social networks; voting; empirical test of theory

\underline{Research question and research area:} Leighley tests then-current theories about how social networks affect political participation. She network size, politicization, and within-network political conflict as predictors of four indicator variables: voting, campaigning, contacting, and 
\underline{Summary of argument and mechanism:} Leighley is carrying out an empirical test of arguments that social networks influence activity. Both she and the theories that she cites seem to have a strong assumption of community homophily.
\underline{Data \& methods:} Data from the 1976 American National Election Study (ANES) survey, in which respondents were asked to list the people with whom they discussed the ``most important national problem.''  I think that the social network IDVs are brought in via a count of discussants and indicator variables for conflict and politicization. Empirical test is a logit model of 724 individuals.
\underline{Findings};
\underline{Notes on related papers or followup:} The conflict measure would be interesting to look at in a multiparty system, with more fluid voting patterns. Would also be interesting to look at network-based diffusion of strategic voting.

\textbf{McAdam, Doug, and Ronnelle Paulsen. 1993. “Specifying the Relationship between Social Ties and Activism.” American Journal Of Sociology 99(3): 640–67.}
